Mechanized Reasoning about a Capability Machine

### 2019-10-16 prisc-2020/paper.tex
abstract draft

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Capability Machines are promising targets for secure compilers since capabilities can be used to enforce abstractions that are usually expected for high-level languages, such as control-flow integrity (CFI) and local state encapsulation (LSE).
  We present the first formalization of a capability machine that supports mechanized reasoning about deep semantic properties, including CFI and LSE.
  Our formalization is done in the Coq implementation of Iris, a state-of-the-art concurrent higher-order separation logic, and includes a formalization of the logical relation defined by Skorstensgaard et. al. \cite{skorstengaardESOP18}, which can used to prove CFI and LSE.
\end{abstract}
